\documentclass[12pt,letterpaper]{article}

\usepackage{ifpdf}
\usepackage{mla}

\begin{document}
\begin{mla}{Minsheng}{Liu}{Marissa Perino}{WCWP 10A}{02/18/16}{Copyright is Necessary}

Has intellectual property become a concept of the past? Indeed, in the
age of Internet, sharing without permission has become a \emph{de facto}
standard, as described by Tomar in his book \emph{Use Me} (85).
Moreover, other people are arguing that the idea of copyright is wrong
in the first place because a new piece of knowledge is always created
from old ones. In his article \emph{Something Borrowed}, Malcolm
Gladwell gently supported the practice of using ``old words'' to
establish ``new ideas'' (127). In \emph{RiP!: A Remix Manifesto}, Brett
Gaylor criticized the copyright laws, showing how the current copyright
protection institution impeded artists' creativity (Gaylor 2008). Though
I partially agree with the view that the domain of copyright should be
limited---more specifically, I disagree with patenting ideas---I insist
that the protection of intellectual property is necessary for soliciting
creativity. Not only does it promote fairness among creators, but it
also protects them from unintended harm. Overall, copyright is more
beneficial than copyleft when done right.

Abstract ideas such as writing a novel in the order reverse to its plot
shouldn't count as intellectual property. Instead, it is the words that
compose the whole story---the commitment part, the hard work of the
author---that should be protected. There are two reasons. First, it is
hard, if not impossible, to find out the inventor of those vague ideas.
In \emph{Something Borrowed}, Gladwell mentioned that the opera writer
Lavery borrowed his phrase ``sins and symptoms,'' even though the phrase
was a quote from Gandhi, who probably learned it from somewhere else
(128). Second, these ideas are scarce. If they are all owned by some
people, others will not be able to create works in the same field. For
example, there are only a few possible plots in spy novels (Widdicombe
52). If they are all patented, authors will have to wait until these
patents expired before writing new spy novels. From this perspective,
protecting general ideas violates the very principle behind the first
copyright law: give incentive to the creator to create \emph{more}
(Gaylor 2008), not \emph{less}.

Why is it important to protect the commitment part of a creative work
then? It matters because it creates a healthy market in which creators
compete in a fair way and contribute works of high qualities. A creator
who has produced an excellent piece of work will likely to have great
works in the future since the previous work has proven the originator's
skills. The society rewards these talented artists with wealth and
reputation as a way to encourage them to create more. Besides, those
without popular creations will be forced out of the market. All these
characteristics of the ``intellectual market'' constitute an implicit
selection process that picks out the best creators. However, declaring
others' commitments as one own---also known as plagiarism---breaks the
game rule. In \emph{The Plagiarist's Tale}, Rowan did a ``literature
mashup''. He wrote a spy novel by copying words from other books
(Widdicombe 53). Since writers' skills depend on their abilities to put
words together, by his mashup Rowan tricked readers into thinking that
he was a capable writer who would produce fantastic novels in the
future. Plagiarism of this type must be eliminated for three reasons.
First, unpunished plagiarism like the one of Rowan would encourage
greedy people to do the same thing. Second, writers who genuinely
deserve acclaims will gain less from their hardworking. Third, the
market could only afford a fixed amount of artists, and when a fake
creator occupies a position in the pool, some potential new star is
going to lose his or her chance. In other words, we might lose a great
artwork merely because someone cheated.

Some people will not be convinced by the above arguments. They may claim
that what we need is a law against plagiarism rather than a law of
copyright. They will argue that if copyright is all about eliminating
illegal ``borrowing'' the society only needs to check whether an author
credit all sources appropriately. In other words, the concept of
copyright should not exist, and everyone can use any intellectual work
freely. However, in the real world creators do need copyright to provide
extra protections for their works. We frequently heard stories about how
authors are hurt by others' abuse of these creations. In \emph{Something
Borrowed}, Gladwell recounted the story of Dorothy Lewis, who found the
opera \emph{Frozen} replicating her life story. She felt extremely
uncomfortable with it because it feels like exposing every secret of her
to the public. Particularly, ``Lewis'' in the opera had an affair that
never took place in the real life, which created severe
misunderstandings between Lewis and her friends (Gladwell 127). One can
also imagine the following fictional story in a world with only an
anti-plagiarism law. An artist named Alice created a lovely cartoon
character. A company used that character in its advertisement without
explicit permission from Alice. Moreover, that company had a bad
reputation. People would naturally think that she endorsed that company.
Not only would Alice feel unjustice---after all, she did nothing
wrong---but she would also feel helpless as she discovered that there
was no law protecting her work.

One might propose to make laws to protect the creators in the above two
examples. However, it is hard to enumerate all possible accidents that
can harm authors, thus making a comprehensive law impossible. This
difficulty is evinced by the fact that the grievance to Dorothy Lewis is
entirely different from that to the fictional Alice. Instead, if we
grant the ownership of a piece of intellectual work to its creator, the
originator could use his or her best knowledge to judge whether it is
appropriate for someone to use that work. In the case of Dorothy Lewis,
she could ask the writer of \emph{Frozen} to take her privacy seriously.
In the fictional example, Alice could directly refuse that company's
request. Therefore, only a law dedicated to copyright protection could
make creators free of fears for future harms so that they can be more
focused on creation itself.

In conclusion, I think the protection of intellectual property is a
necessity, regardless the way we distribute and consume creative works.
The purpose of copyright is to encourage more creative works rather than
obstructing creativity. Ideas should not be protected, since it is
unhelpful, it not harmful, to a creative society. Instead, we should
protect the hard work of creators so that a fair environment for
creation can be promoted and creators can be protected from unexpected
harms.

\begin{workscited}
\bibent Widdicombe, Lizzie. ``The Plagiarist's Tale.'' \textit{The New Yorker}.
Feb. 13 \& 20, 2012. Print.

\bibent Gladwell, Malcolm. ``Something Borrowed.'' \textit{The New Yorker}.
22 Nov. 2004. Web. 10 May 2011.

\bibent Tomar, Dave. ``Use Me.'' \textit{The Shadow Scholar: How I Made a Living
  Helping College Kids Cheat}.
New York: Bloomsbury, 2012. 79 -- 87. Print.

\bibent Gaylor, Brett, et al. ``RiP!: A Remix Manifesto.'' Web. 2008.
\end{workscited}
\end{mla}
\end{document}
